### 2022-10-31 Draft_GFC.tex
Last version  31/10

% where $b_{i} = \begin{cases}0 \; \text{if} \; \gamma = 0 \\ 1 \; \text{else} \end{cases}$, for each sample $\Gamma_{1}, \ldots, \Gamma_{d}$ they determine a mean vector of length $r$ and mean angle $\hat{\Phi}$, (They just sample from the same image $Z_{l,l}$...). They use the standard ellipse to analyses these statistics. Hum this is what they say about this \textit{The tips of the vectors of a second order
% sample form a scatter diagram of data with
% standard deviations in the $X$ and $Y$ directions and a
% certain trend upward or downward. The standard ellipse
% describes this behavior in a condensed way: assuming
% normality, roughly $40\%$ of data points fall inside the
% ellipse and $60\%$ of them outside. The parent population
% does not need to be normal, although it is desirable that
% it does not deviate from normality too much.}
% They define the standard ellipse in the following way
% \begin{itemize}
%   \item its center $(\hat{x}, \hat{y})$ \\
%   \item Construct a rectangle with center at $(\hat{x}, \hat{y})$ and sides parallel to the $X$ and $Y$ axes.. 
%   \item the standard ellipse is embedded in the rectangle above (see the article for more details on the construction). 
  % \end{itemize}

@@

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ and for $x \in G_{m}$, we define $C_{m}(x)$ as
\begin{equation*}
C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
\end{equation*}
The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3,4}{
  \foreach \y in {0,1,2,3,4}{
  \draw[fill = red] (\x,\y) circle (2pt);
  } 
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $G_{m}$.}
\label{fig1}
\end{figure}

\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in G_m}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
\begin{figure}[H]
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, Using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
\end{figure}
Let us consider a threshold parameter $t \in \mathbb{R}$. We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in G_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

@@

For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{x: w_{i}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$. Then, the perimeter of the binary image $Z$ is given by

@@

We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field and $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ with $\rho(e_i) \in [-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1)}_{m}(t)\right) + \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)\right)$  and
if $\rho(e_{i}) \in ]-1,1]$, 

@@

@@

\begin{remark}(degenerative case)
If  $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$
the function $t \mapsto \mathbb{E}\left(f^{(i)}(t) \right)$ is even.

@@

Let us start with the case where $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since

@@

\left\{ x \in G_{m}; w_{i}(x) \subset (0,m)^{2}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 

@@

 We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation} \label{expressions} \Delta^{i}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{i}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation}
The covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}

@@

Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_1)  \end{pmatrix}$, which directly  implies that the two variables are independent.

@@

&= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, X_{e_i} -X_{\scriptscriptstyle 0}) \leq t -X_{\scriptscriptstyle 0}\leq \max(0, X_{e_i}-X_{0})\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}) \leq t + \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}\leq \max(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0})\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}) \leq t - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}\leq \max(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2})\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right). \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}  \leq Y \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right)

@@

with $N, Y \sim \mathcal{N}(0,I_{2})$, thus 

@@

& \hspace{-6cm}= \mathbb{P}\left(-|N| < t \leq |N|\right) = \cfrac{2}{\sqrt{2\pi}} \int_{\scriptscriptstyle 0}^{+\infty} \mathbbm{1}_{\left\{-z < t \leq z\right\}} e^{-\frac{z^2}{2}}dz  = \cfrac{2}{\sqrt{2\pi}} \int_{\scriptscriptstyle 0}^{+\infty} \mathbbm{1}_{\left\{t \leq z\right\}} e^{-\frac{z^2}{2}}dz \\
& \hspace{-6cm}= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).

@@

The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$.

@@

The first moment of the total variation is given by the sum over the two directions of Equation \eqref{totalvariation}. 

@@

Study of the behavior of the nodal curve $t = 0$, 

@@

Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 

@@

 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right).

@@

@@

Note that $\rho \mapsto \sqrt{1-\rho}$ is strictly decreasing similarly  for level $0$, one has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - 1$, since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing. 

@@

Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 

@@

Let $s, t \in \mathbb{R}$ such that $t \leq s$. Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.

@@

\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + 2\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .

@@

To simplify the notations, we chose to do the computations for direction $i =1$. Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$ for $t \leq s$. 

@@

\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))& = \text{Cov}\left( \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}}f_{t}^{\scriptscriptstyle (1)}(x), \sum_{y, w_{1}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} f_{s}^{\scriptscriptstyle (1)}(y)\right) \\
& = \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \sum_{y, w_{1}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right).

@@

By the stationarity hypothesis, one has $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right)= \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(y-x) \right)$. Then 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right)

@@

for $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has

@@

Again, considering $z_1 = y_1 - x_1$
1 \leq y_1 \leq m-1 
1 -x_1 \leq z_1 \leq m- 1 - x_1
2 - m \leq z_1 \leq m-1 \hspace{2.5cm}  \\
\max(0, 1-z_1) \leq x_1 \leq \min(m-1 , m-1-z_1),
\end{array}\right.
and, $z_{2} = y_{2}-x_{2}$
0 \leq y_2 \leq m-1 
1 \leq x_2 \leq m-1 \hspace{0.7cm} \\
-x_2 \leq z_2 \leq m- 1 - x_2
1 - m \leq z_2 \leq m-2 \hspace{2.5cm}  \\
\max(1, -z_2) \leq x_2 \leq \min(m-1 , m-1-z_2)

@@

The case $x=0$ is a special case, in order to compute it, we just have to apply the same strategy we used to compute the first moment in \ref{propFisrtmoment}, thus we get,

@@

And, 

@@

\subsection{Three and four cells configuration}

@@

>>>>

\end{equation*}We debi

@@

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in G_{m}$, we define $C_{m}(x)$ as
\begin{equation*}
C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
\end{equation*}
The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3}{
  \foreach \y in {0,1,2,3}{
  \draw[fill = red] (\x,\y) circle (2pt);
  } 
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $G_{m}$.}
\label{fig1}
\end{figure}

\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in G_m}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
\begin{figure}[H]
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
\end{figure}
Let us consider a threshold parameter $t \in \mathbb{R}$. We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in G_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

@@

For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$. Then, the perimeter of the binary image $Z$ is given by

@@

We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and
  \item if $\rho(e_{i}) \in ]-1,1]$, 

@@

\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$

@@

\textcolor{blue}{\begin{remark}
Note that $\mathbb{E}\left(f^{(i)}(t) \right) = 0$ in the case where $\rho(e_i) = 1$ 
\end{remark}}

@@

Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since

@@

\left\{ x \in G_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 

@@

 We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation*}
Let us introduce the following Lemma, 
\label{lemmasommediff}
Let $a,b,t \in \mathbb{R}$, then 
$$\min(a,b) \leq t \leq \max(a,b) \iff\left|t - \frac{a+b}{2}\right| \leq \left| \frac{ b-a }{2}\right| $$
\min(a,b) \leq t \leq \max(a,b) & \leftrightarrow \min(0, b - a) \leq t - a \leq \max(0, b - a) \\
& \iff \min(0, b - a) \leq t + \frac{b-a - (b+a)}{2} \leq \max(0, b - a) \\
& \iff\min(- \frac{b-a}{2}, \frac{b - a}{2}) \leq t -\frac{b+a}{2} \leq \max(- \frac{b-a}{2}, \frac{b-a}{2}) \\
& \iff - \frac{\left|b-a\right|}{2} \leq t -\frac{b+a}{2} \leq + \frac{\left|b-a\right|}{2} \\
& \iff \left|t -\frac{b+a}{2}\right| \leq \frac{\left|b-a\right|}{2}
Thus, applying the Lemma we get 
& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
\end{align*}}Besides, the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}

@@

Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent, we get the following system 
  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1-\rho(e_i))}U, \textcolor{white}{(1-\rho(e_i))U + }\\
  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \textcolor{white}{(1-\rho(e_i))U + } \sqrt{2(1+\rho(e_i)}V, 
\end{array}
\right.$

@@

\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq 2t - \sqrt{2(1+\rho(e_i)}V \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}  \leq V \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right), 

@@

with $U, V \sim \mathcal{N}(0,I_{2})$, thus 

@@

& = \mathbb{P}\left(|t| \leq |N|\right) = 2\left(1 - \Phi\left(|t|\right)\right).

@@

The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$ .

@@

@@

@@

Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter of the nodal curve ($t=0$).

@@

 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right),

@@

where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 

@@

One has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) -~1$. Since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing. 

@@

Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter at level $t$:

@@

Let $s, t \in \mathbb{R}$ such that $t \leq s$. Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.

@@

\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \\
& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .

@@

Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$ for $t \leq s$. 

@@

\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))& = \sum_{x, w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle (1)}_{m}} \sum_{y, w_{1}(y) \in \mathbb{E}^{\scriptscriptstyle (1)}_{m}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right).

@@

By stationarity, one has $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right)= \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(y-x) \right)$, 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right).

@@

For $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has

@@

Again, considering $z_1 = y_1 - x_1$ and, $z_{2} = y_{2}-x_{2}$, we get

@@

@@

where, 

@@

@@

\draw[pattern=north east lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
\draw[pattern=north west lines, pattern color=green, opacity=1] (0, 0) rectangle (0.5,0.5);
